Think deep for reef resilience

### 2025-07-11 paper/paper_draft.qmd
Introduce uncertainty exploration of carbonate budget in narrative

Using median coral cover timeseries for each reef we calculated the number of years each
reef maintains coral cover above these live coral cover threshold levels, inferring the
number of years each reef maintains a net positive carbonate budget, accumulating reef
framework. As in situ carbonate budgets are influenced by a range of processes, our
calculations of carbonate budget maintainence are intended as estimates and do not reflect
the conditions that will be experienced on a reef, but indicate relative levels of health
across reefs. To capture the wide influence of environmental factors on carbonate budget
levels, we analyse live coral cover thresholds required for positive carbonate budgets from
10 to 20% (inclusive, at step 1%).

The distribution of number of years above carbonate-cover thresholds is right-skewed, with
many reefs experiencing low numbers of years above thresholds. Similarly, reef median depth
levels and log (natural) total connectivity strength levels follow right-skewed
distributions. Therefore, we analyse the correlation between number of years above
carbonate-cover thresholds and these characteristics using Spearman's correlation
coefficient.

>>>>

Using median coral cover timeseries for each reef we calculated the number of years each
reef maintains coral cover above a given percent threshold. The threshold represents the
level of live coral cover necessary to maintain a positive carbonate budget (denoted here as
$\beta_{0}$ to indicate the budget equilibrium). Greater number of years above $\beta_{0}$
therefore suggests greater resilience and opportunity for recovery.

Recent analyses suggest a general threshold of ~17% live coral cover in the case of
the GBR [@desbiens]. Given in situ carbonate budgets are influenced by (1) a range of
processes; (2) the variety of approaches that could be used to measure those processes; and
(3) the uncertainty surrounding these, it would be unreasonable to assume all
reefs adhere to a single precise $\beta_{0}$ value. Concurrently, it is difficult to
ascertain a suitable $\beta_{0}$ value for each individual reef.

Given the uncertainties present, the proportion of reefs that display capacity to maintain
coral cover above a given $\beta_{0}$ threshold is examined. An indicative range of 10 to
20% is used (inclusive, with a step size of 1%). The range was informed by Perry et al.,
[-@perry2015] and Desbians et al., [-@desbiens] providing indications of the lower and upper
bounds respectively. Spearman's correlation coefficient was adopted to assessed the
relationship between connectivity strength and the number of years above $\beta_{0}$.
The process was then repeated with median reef depth.

<!-- Split and move below to results/discussion -->
The distribution of number of years above carbonate-cover thresholds is right-skewed, with
many reefs experiencing low numbers of years above thresholds. Similarly, reef median depth
levels and natural log total connectivity strength levels follow right-skewed
distributions. Therefore, we analyse the correlation between number of years above
carbonate-cover thresholds and these characteristics using Spearman's correlation
coefficient.
